QOCO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2023-10-16 paper-conference.tex
F_revision_3

\subsection{DQN-based solution}
We utilize the DQN technique to find the mapping between each state-action pair to Q-values in the formulated MDP. As shown in Fig.~\ref{DQN}, each MD $i \in \mathcal{I}$ is equipped with a neural network comprising six layers. These layers include an input layer, an LSTM layer, two dense layers, an advantage-value (A\&V) layer, and an output layer. The parameter vector $\theta_i$ of MD $i$'s neural network is defined to maintain the connection weights and neuron biases across all layers. For MD $i \in \mathcal{I}$, we utilize the state information as the input of neural network. The state information $\lambda_i(t)$, $\delta_i^{\text{C}}(t)$, $\delta_i^{\text{T}}(t)$, $\phi_i(t)$, and $\boldsymbol{\eta}_i^{\text{E}}(t-1)$ are directly passed to the dense layer, while the state information $\mathcal{H}(t)$ is first directed to the LSTM layer and then the resulting output is sent to the dense layer. The role and responsibilities of each layer are detailed as follows.

\subsubsection{Predicting Workloads at ENs}
In order to capture the dynamic behavior of workloads at the ENs, we employ the LSTM network \cite{hochreiter1997long}. This network maintains a memory state $\mathcal{H}(t)$ that evolves over time, enabling neural network to predict future workloads at the ENs based on historical data. By taking the matrix $\mathcal{H}(t)$ as an input, the LSTM network learns the patterns of workload dynamics. The architecture of the LSTM consists of $T^{\text{s}}$ units, each equipped with a set of hidden neurons, and it processes individual rows of the matrix $\mathcal{H}(t)$ sequentially. Through this interconnected design, they track the variations in sequences from $\boldsymbol{h}_1(t)$ to $\boldsymbol{h}_{T^{\text{s}}}(t)$, where $\boldsymbol{h}_i(t) = (h_{i,j}(t), j \in \mathcal{J})$, thereby revealing workload fluctuations at the ENs across different time slots. The final LSTM unit produces output that encapsulates the anticipated workload dynamics, and this output is then connected to the subsequent layer neurons for further learning.

@@

The A\&V layer consists of two distinct dense networks referred to as network A and network V. Network A's role is to learning the action-advantage value  for each action, while network V focuses on learning the state-value. For an MD $i \in \mathcal{I}$, we define $V_i(\boldsymbol{s}_i(t); \theta_i)$ and $A_i(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta_i)$ to denote the state-value and the action-advantage value of action $\boldsymbol{a} \in \mathcal{A}$ under state $\boldsymbol{s}_i(t) \in \mathcal{S}$, respectively. The parameter vector $\theta_i$ is responsible for determining these values, and it can be adjusted and subjected to training in the QOCO algorithm.

@@

The QOCO algorithm has been meticulously designed to optimize the allocation of computational tasks between MDs and ENs. Since the training of neural networks imposes an extensive computational workload on MDs, we enable MDs to utilize ENs for training their neural networks, effectively reducing their computational workload. For each MD $i \in \mathcal{I}$, there is an associated EN, denoted as $j_i \in \mathcal{J}$, which assists in the training process. This EN possesses the highest transmission capacity among all ENs. We define $\mathcal{I}_j \subset \mathcal{I}$ as the set of MDs for which training is executed by EN $j \in \mathcal{J}$, i.e. $\mathcal{I}_j = \{i \in \mathcal{I} | j_i = j\}$. This approach is feasible due to the minimal information exchange and processing requirements for training compared to MD's tasks. The QOCO algorithm to be executed at MD $i \in \mathcal{I}$ and EN $j \in \mathcal{J}$ are given in Algorithms ~\ref{alg:cap} and ~\ref{alg:cap2}, respectively. The core concept involves training neural networks with MD experiences (i.e., state, action, QoE, next state) to map Q-values to each state-action pairs. This mapping allows MD to identify the action in the observed state with the highest Q-value and maximize its long-term QoE.

In detail, the EN $j \in \mathcal{J}$ maintains a replay buffer $\mathcal{M}_i$ with two neural networks for MD $i$: $\textit{Net}_i^{\text{E}}$, denoting the evaluation network, and $\textit{Net}_i^{\text{T}}$, denoting the target network, which have the same neural network architecture. However, they possess distinct parameter vectors $\theta^{\text{E}}_i$ and $\theta^{\text{T}}_i$, respectively. Their Q-values are represented by $Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$ and $Q_i^{\text{T}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{T}}_i)$ for the MD $i \in \mathcal{I}_j$, associating the action $\boldsymbol{a} \in \mathcal{A}$ under the state $\boldsymbol{s}_i(t) \in \mathcal{S}$, respectively. The replay buffer records the observed experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ of the MD $i$ for some $t \in \mathcal{T}$. The $\textit{Net}_i^{\text{E}}$ is responsible for action selection, while the $\textit{Net}_i^{\text{T}}$ characterizes the target Q-values, which represent the estimated long-term QoE resulting from an action in the observed state. The target Q-value serves as the reference for updating the network parameter vector $\theta^{\text{E}}_i$. This update occurs through the minimization of disparities between the Q-values under $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$. In the following, we introduce the offloading decision algorithm in MD $i \in \mathcal{I}$ and the training process algorithm in EN $j \in \mathcal{J}$, respectively.

@@

\subsubsection{Offloading Decision Algorithm at MD $i \in \mathcal{I}$}
 We analyze a series of episodes, where $\textit{Ep.}$ denote the number of them. At the start of each episode, if MD $i \in \mathcal{I}$ receives a new task arrival $z_i(t)$, it initializes the state $\mathcal{S}_i(1)$ and sends a $\textit{UpdateRequest}$ to EN $n_i$. After receiving the requested parameter vector $\theta_i^{\text{E}}$ of $\textit{Net}_i^{\text{E}}$ from EN $j_i$, MD $i$ selects its action for task $z_i(t)$ in the following manner:
\begin{alignat}{2}
	\hspace*{-2mm}\boldsymbol{a}_i(t) \hspace*{-0.5mm} = \hspace*{-0.5mm}
	\begin{cases} 
		\text{arg $\max_{\boldsymbol{a}\in \mathcal{A}}Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$,} &	\hspace*{-3mm} \text{with $\boldsymbol{\text{p}}(1 -\boldsymbol{\epsilon})$,} \\
 	\text{pick an random action from $\mathcal{A}$,} & \hspace*{-3mm} \text{with $\boldsymbol{\text{p}}(\boldsymbol{\epsilon})$,}
	\end{cases}
	\label{26}  
\end{alignat}
where $\boldsymbol{\text{p}}(\cdot)$ is probability, and $\boldsymbol{\epsilon}$ represents the random exploration probability. The value of $Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$ indicates the Q-value under the parameter $\theta^{\text{E}}_i$ of the neural network $\textit{Net}_i^{\text{E}}$. Specifically, the MD with a probability of $1 - \boldsymbol{\epsilon}$ selects the action associated with the highest Q-value under $\textit{Net}_i^{\text{E}}$ in the observed state $\boldsymbol{s}_i(t)$.
\begin{algorithm} [tbp]
	\caption{QOCO Algorithm (Offloading Decision)}\label{alg:cap}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\Require state space $\mathcal{S}$, action space $\mathcal{A}$
		\Ensure MD $i \in \mathcal{I}$ experience 
		\For {episode from 1 to \textit{Ep.}}
		\State Initialize $\boldsymbol{s}_i(1)$
		\For {time slot $t \in \mathcal{T}$}
		\If{MD $i$ receives a new task $z_i(t)$}
		\State Send a \textit{UpdateRequest} to EN $j_i$;
		\State Receive network parameter vector $\theta_i^{\text{E}}$;
		\State Select action $\boldsymbol{a}_i(t)$ based on the equation \eqref{26};
		\EndIf
		\State Observe a set of QoEs $\{\boldsymbol{q}_i(t'), t' \in \mathcal{F}_i^t\}$;
		\State Observe\textcolor{white}{i}the next\textcolor{white}{i}state $\textbf{\textit{s}}_i(t+1)$;\textcolor{white}{i}
		\For {each task $z_i(t')$ where $t' \in \mathcal{F}_i^t$} 
		\State Send \hspace{-1mm} $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ to $j_i$;
		\EndFor
		\EndFor
		\EndFor
	\end{algorithmic}
\end{algorithm}

In the next time slot $t+1$, MD $i$ observes the state $\mathcal{S}_i(t+1)$. However, due to the potential for tasks to extend across multiple time slots, the QoE $\boldsymbol{q}_i(t)$ associated with task $z_i(t)$ may not be observable in time slot $t+1$. On the other hand, MD $i$ may observe a group of QoEs associated with some tasks $z_i(t')$ in time slots $t' \leq t$. For each MD $i$, we define the set $\mathcal{F}_i^t \subset \mathcal{T}$ to denote the time slots during which each arrival task $z_i(t')$ is either processed or dropped at time slot $t$, as given by:\\

@@

\begin{algorithm}[tbp]
	\caption{QOCO Algorithm (Training Process)}\label{alg:cap2}
	\begin{algorithmic}[1]
		\State Initialize replay buffer $\mathcal{M}_i$ for each MD $i \in \mathcal{I}_j$;
		\State Initialize $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ with random parameters $\theta_i^{\text{E}}$ and $\theta_i^{\text{T}}$ respectively, for each MD $i \in \mathcal{I}_j$;
		\State Set Count := 0
		\While{True} \Comment{\textit{infinite loop}}
		\If{receive a \textit{UpdateRequest} from MD $i \in \mathcal{I}_j$}
		\State Send  $\theta_i^{\text{E}}$ to MD $i \in \mathcal{I}$;
		\EndIf
		\If {receive an experience \hspace{-0.2mm} $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$ \\ \;\;\;\; from MD $i \in \mathcal{I}_j$}
		\State Store $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ in $\mathcal{M}_i$;
		\State Get a collection of experiences  $\mathcal{I}$ from $\mathcal{M}_i$; 
		\For{each experience $i \in \mathcal{I}$} 
		\State Get experience $(\boldsymbol{s}_i(\hspace{-0.2mm}i\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}i\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}i\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}i\hspace{-0.5mm}+1\hspace{-0.2mm}))$; 
		\State Create $\hat{Q}_{i,i}^{\text{T}}$ according to   \eqref{28};
		\EndFor
		\State Set vector  $\hat{\mathbf{Q}}_i^{\text{T}} := (\hat{Q}^{\text{T}}_{i,i}, i \in \mathcal{I})$;
		\State Update $\theta_i^{\text{E}}$ to minimize $L(\theta_i^{\text{E}}$, $\hat{\mathbf{Q}}_i^{\text{T}})$ in   \eqref{30};
		\State Count := Count + 1;
		\If {mod(Count, \textit{ReplaceThreshold}) = 0}
		\State $\theta_i^{\text{T}}$ := $\theta_i^{\text{E}}$;
		\EndIf
		\EndIf
		\EndWhile

@@

\subsubsection{Training Process Algorithm at EN $j \in \mathcal{J}$}
Upon initializing the replay buffer $\mathcal{M}_i$ with the neural networks $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ for each MD $i \in \mathcal{I}_j$, the EN $j \in \mathcal{J}$ waits for messages from the MDs in the set $\mathcal{I}_j$. When EN $j$ receives a $\textit{UpdateRequest}$ signal from a MD $i \in \mathcal{I}_j$, it responds by transmitting the updated parameter vector $\theta^{\text{E}}_i$, obtained from $\textit{Net}_i^{\text{E}}$, back to MD $i$. On the other side, if EN $j$ receives an experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ from MD $i \in \mathcal{I}_j$, the EN stores this experience in the replay buffer $\mathcal{M}_i$ associated with that MD. The replay buffer operates at maximum capacity and FIFO principle.

The EN randomly selects a sample collection of experiences from the replay buffer, denoted as $\mathcal{N}$. For each experience $n \in \mathcal{N}$, it calculates the value of $	\hat{Q}^{\text{T}}_{i,n}$. This value represents the QoE in experience $n$ and includes a discounted Q-value of the action anticipated to be taken in the subsequent state of experience $n$, according to the network $\textit{Net}^\text{T}_i$, given by
\begin{alignat}{2}
	\hat{Q}_{i,n}^{\text{T}} = \boldsymbol{q}_i(n) + \gamma Q_i^{\text{T}}(\boldsymbol{s}_i(n+1)), \tilde{\boldsymbol{a}}_n; \theta_i^{\text{T}}),
	\label{28}  
\end{alignat}  
where $\tilde{\boldsymbol{a}}_n$ denotes the optimal action for the state $\boldsymbol{s}_i(n+1)$ based on its highest Q-value under $\textit{Net}_i^{\text{E}}$, as given by:
\begin{alignat}{2}
	\tilde{\boldsymbol{a}}_n = \text{arg} \; \max_{\boldsymbol{a} \in \mathcal{A}} \; Q_i^{\text{E}}(\boldsymbol{s}_i(n+1), \boldsymbol{a}; \theta_i^{\text{E}}).
	\label{29}  
\end{alignat} 
In particular, regarding the experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for the action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. %based on $\textit{Net}_i^{\text{T}}_i$, i.e., $\gamma Q_i^{\text{T}}(\mathcal{S}_i(i+1)), \mathcal{A}_i^{\text{N}}; \theta_i^{\text{T}})$
Based on the set $\mathcal{N}$, the EN trains the MD's neural network using previous sample experiences. Simultaneously, it updates $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ and computes $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n}, n \in \mathcal{N})$. The key idea of updating $\textit{Net}_i^{\text{E}}$ is minimizing the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
\begin{alignat}{2}
	\hspace{-2mm}L(\theta_i^{\text{E}},\hat{\mathbf{Q}}_i^{\text{T}}) = {1 \over |\mathcal{N}| }\hspace{-1mm} \sum\limits_{n \in \mathcal{N}} \bigg(Q_i^{\text{E}}(\boldsymbol{s}_i(n) , \boldsymbol{a}_i(n); \theta_i^{\text{E}} ) -   \hat{Q}^{\text{T}}_{i,n}  \bigg)^2.
	\label{30}  
\end{alignat}  
Every \textit{ReplaceThreshold} iterations, the update of $\textit{Net}_i^{\text{T}}$ will involve duplicating the parameters from $\textit{Net}_i^{\text{E}}$ ($\theta_i^{T} = \theta_i^{E}$). The objective is to consistently update the network parameter $\theta_i^{T}$ in $\textit{Net}_i^{\text{T}}$, which enhances the approximation of the long-term QoE when computing the target Q-values in \eqref{28}.

>>>>

\subsection{DQN-based solution}
We utilize the DQN technique to find the mapping between each state-action pair to Q-values in the formulated MDP. As shown in Fig.~\ref{DQN}, each MD $i \in \mathcal{I}$ is equipped with a neural network comprising six layers. These layers include an input layer, an LSTM layer, two dense layers, an advantage-value (A\&V) layer, and an output layer. The parameter vector $\theta_i$ of MD $i$'s neural network is defined to maintain the connection weights and neuron biases across all layers. For MD $i \in \mathcal{I}$, we utilize the state information as the input of neural network. The state information $\lambda_i(t)$, $\delta_i^{\text{C}}(t)$, $\delta_i^{\text{T}}(t)$, $\phi_i(t)$, and $\boldsymbol{\eta}_i^{\text{E}}(t-1)$ are directly passed to the dense layer, while the state information $\mathcal{H}(t)$ is first supplied to the LSTM layer and then the resulting output is sent to the dense layer. The role and responsibilities of each layer are detailed as follows.

\subsubsection{Predicting Workloads at ENs}
In order to capture the dynamic behavior of workloads at the ENs, we employ the LSTM network \cite{hochreiter1997long}. This network maintains a memory state $\mathcal{H}(t)$ that evolves over time, enabling neural network to predict future workloads at the ENs based on historical data. By taking the matrix $\mathcal{H}(t)$ as an input, the LSTM network learns the patterns of workload dynamics. The architecture of the LSTM consists of $T^{\text{s}}$ units, each equipped with a set of hidden neurons, and it processes individual rows of the matrix $\mathcal{H}(t)$ sequentially. Through this interconnected design, the MD track the variations in sequences from $\boldsymbol{h}_1(t)$ to $\boldsymbol{h}_{T^{\text{s}}}(t)$, where vector $\boldsymbol{h}_i(t) = (h_{i,j}(t))_{j \in \mathcal{J}}$, thereby revealing workload fluctuations at the ENs across different time slots. The final LSTM unit produces an output that encapsulates the anticipated workload dynamics, and is then connected to the subsequent layer neurons for further learning.

@@

The A\&V layer consists of two distinct dense networks referred to as network A and network V. Network A's role is to learn the action-advantage value  for each action, while network V focuses on learning the state-value. For an MD $i \in \mathcal{I}$, we define $V_i(\boldsymbol{s}_i(t); \theta_i)$ and $A_i(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta_i)$ to denote the state-value and the action-advantage value of action $\boldsymbol{a} \in \mathcal{A}$ under state $\boldsymbol{s}_i(t) \in \mathcal{S}$, respectively. The parameter $\theta_i$ is responsible for determining these values, and it can be adjusted when training the QOCO algorithm.

@@

The QOCO algorithm is meticulously designed to optimize the allocation of computational tasks between MDs and ENs. Since the training of neural networks imposes an extensive computational workload on MDs, we enable MDs to utilize ENs for training their neural networks, effectively reducing their computational workload. For each MD $i \in \mathcal{I}$, there is an associated EN, denoted as $j_i \in \mathcal{J}$, which assists in the training process. This EN possesses the highest transmission capacity among all ENs. We define $\mathcal{I}_j \subset \mathcal{I}$ as the set of MDs for which training is executed by EN $j \in \mathcal{J}$, i.e. $\mathcal{I}_j = \{i \in \mathcal{I} | j_i = j\}$. This approach is feasible due to the minimal information exchange and processing requirements for training compared to MD's tasks. The algorithms to be executed at MD $i \in \mathcal{I}$ and EN $j \in \mathcal{J}$ are given in Algorithms ~\ref{alg:cap} and ~\ref{alg:cap2}, respectively. The core concept involves training neural networks with MD experiences (i.e., state, action, QoE, next state) to map Q-values to each state-action pair. This mapping allows MD to identify the action in the observed state with the highest Q-value and maximize its long-term QoE.

In detail, EN $j \in \mathcal{J}$ maintains a replay buffer denotes as $\mathcal{M}_i$ with two neural networks for MD $i$: $\textit{Net}_i^{\text{E}}$, denoting the evaluation network, and $\textit{Net}_i^{\text{T}}$, denoting the target network, which have the same neural network architecture. However, they possess distinct parameter vectors $\theta^{\text{E}}_i$ and $\theta^{\text{T}}_i$, respectively. Their Q-values are represented by $Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$ and $Q_i^{\text{T}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{T}}_i)$ for MD $i \in \mathcal{I}_j$, respectively, associating the action $\boldsymbol{a} \in \mathcal{A}$ under the state $\boldsymbol{s}_i(t) \in \mathcal{S}$. The replay buffer records the observed experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ of MD $i$. Moreover, $\textit{Net}_i^{\text{E}}$ is responsible for action selection, while $\textit{Net}_i^{\text{T}}$ characterizes the target Q-values, which represent the estimated long-term QoE resulting from an action in the observed state. The target Q-value serves as the reference for updating the network parameter vector $\theta^{\text{E}}_i$. This update occurs through the minimization of disparities between the Q-values under $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$. In the following, we introduce the offloading decision algorithm of MD $i \in \mathcal{I}$ and the training process algorithm running in EN $j \in \mathcal{J}$.

@@

\subsubsection{Offloading Decision Algorithm at MD $i \in \mathcal{I}$}
 We analyze a series of episodes, where $N^{\text{ep}}$ denotes the number of them. At the beginning of each episode, if MD $i \in \mathcal{I}$ receives a new task $z_i(t)$, it initializes the state $\mathcal{S}_i(1)$ and sends an $\textit{UpdateRequest}$ to EN $n_i$. After receiving the requested parameter vector $\theta_i^{\text{E}}$ of $\textit{Net}_i^{\text{E}}$ from EN $j_i$, MD $i$ chooses the following action for task $z_i(t)$.
\begin{alignat}{2}
	\hspace*{-2mm}\boldsymbol{a}_i(t) \hspace*{-0.5mm} = \hspace*{-0.5mm}
	\begin{cases} 
		\text{arg $\max_{\boldsymbol{a}\in \mathcal{A}}Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$,} & \text{w.p. $1-\boldsymbol{\epsilon}$,} \\
 	\text{pick a random action from $\mathcal{A}$,} & \text{w.p. $\boldsymbol{\epsilon}$,}
	\end{cases}
	\label{26}  
\end{alignat}
where w.p. stands for with probability, and $\boldsymbol{\epsilon}$ represents the random exploration probability. The value of $Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$ indicates the Q-value under the parameter $\theta^{\text{E}}_i$ of the neural network $\textit{Net}_i^{\text{E}}$. Specifically, the MD with a probability of $1 - \boldsymbol{\epsilon}$ selects the action associated with the highest Q-value under $\textit{Net}_i^{\text{E}}$ in the observed state $\boldsymbol{s}_i(t)$.
\begin{algorithm} [tbp]
	\caption{QOCO Algorithm (Offloading Decision)}\label{alg:cap}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\Require state space $\mathcal{S}$, action space $\mathcal{A}$
		\Ensure MD $i \in \mathcal{I}$ experience 
		\For {episode 1 to $N^{\text{ep}}$}
		\State Initialize $\boldsymbol{s}_i(1)$
		\For {time slot $t \in \mathcal{T}$}
		\If{MD $i$ receives a new task $z_i(t)$}
		\State Send an \textit{UpdateRequest} to EN $j_i$;
		\State Receive network parameter vector $\theta_i^{\text{E}}$;
		\State Select action $\boldsymbol{a}_i(t)$ based on \eqref{26};
		\EndIf
		\State Observe a set of QoEs $\{\boldsymbol{q}_i(t'), t' \in \mathcal{F}_i^t\}$;
		\State Observe\textcolor{white}{i}the next\textcolor{white}{i}state $\textbf{\textit{s}}_i(t+1)$;\textcolor{white}{i}
		\For {each task $z_i(t')$ where $t' \in \mathcal{F}_i^t$} 
		\State Send \hspace{-1mm} $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ to $j_i$;
		\EndFor
		\EndFor
		\EndFor
	\end{algorithmic}
\end{algorithm}

In the next time slot $t+1$, MD $i$ observes the state $\mathcal{S}_i(t+1)$. However, due to the potential for tasks to extend across multiple time slots, QoE $\boldsymbol{q}_i(t)$ associated with task $z_i(t)$ may not be observable in time slot $t+1$. On the other hand, MD $i$ may observe a group of QoEs associated with some tasks $z_i(t')$ in time slots $t' \leq t$. For each MD $i$, we define the set $\mathcal{F}_i^t \subset \mathcal{T}$ to denote the time slots during which each arriving task $z_i(t')$ is either processed or dropped in time slot $t$, as given by:\\

@@

\begin{algorithm}[tbp]
	\caption{QOCO Algorithm (Training Process)}\label{alg:cap2}
	\begin{algorithmic}[1]
		\State Initialize replay buffer $\mathcal{M}_i$ for each MD $i \in \mathcal{I}_j$;
		\State Initialize $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ with random parameters $\theta_i^{\text{E}}$ and $\theta_i^{\text{T}}$ respectively, for each MD $i \in \mathcal{I}_j$;
		\State Set Count := 0
		\While{True} \Comment{\textit{infinite loop}}
		\If{receive an \textit{UpdateRequest} from MD $i \in \mathcal{I}_j$}
		\State Send  $\theta_i^{\text{E}}$ to MD $i \in \mathcal{I}$;
		\EndIf
		\If {an experience \hspace{-0.2mm} $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$ is received \\ \;\;\;\; from MD $i \in \mathcal{I}_j$}
		\State Store $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ in $\mathcal{M}_i$;
		\State Get a collection of experiences  $\mathcal{I}$ from $\mathcal{M}_i$; 
		\For{each experience $i \in \mathcal{I}$} 
		\State Get experience $(\boldsymbol{s}_i(\hspace{-0.2mm}i\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}i\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}i\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}i\hspace{-0.5mm}+1\hspace{-0.2mm}))$; 
		\State Generate $\hat{Q}_{i,i}^{\text{T}}$ according to   \eqref{28};
		\EndFor
		\State Set vector  $\hat{\mathbf{Q}}_i^{\text{T}} := (\hat{Q}^{\text{T}}_{i,i}, i \in \mathcal{I})$;
		\State Update $\theta_i^{\text{E}}$ to minimize $L(\theta_i^{\text{E}}$, $\hat{\mathbf{Q}}_i^{\text{T}})$ in   \eqref{30};
		\State Count := Count + 1;
		\If {mod(Count, \textit{ReplaceThreshold}) = 0}
		\State $\theta_i^{\text{T}}$ := $\theta_i^{\text{E}}$;
		\EndIf
		\EndIf
		\EndWhile

@@

\subsubsection{Training Process Algorithm at EN $j \in \mathcal{J}$}
Upon initializing the replay buffer $\mathcal{M}_i$ with the neural networks $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ for each MD $i \in \mathcal{I}_j$, EN $j \in \mathcal{J}$ waits for messages from the MDs in the set $\mathcal{I}_j$. When EN $j$ receives an $\textit{UpdateRequest}$ signal from an MD $i \in \mathcal{I}_j$, it responds by transmitting the updated parameter vector $\theta^{\text{E}}_i$, obtained from $\textit{Net}_i^{\text{E}}$, back to MD $i$. On the other side, if EN $j$ receives an experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ from MD $i \in \mathcal{I}_j$, the EN stores this experience in the replay buffer $\mathcal{M}_i$ associated with that MD. %The replay buffer operates at maximum capacity and FIFO principle.

The EN randomly selects a sample collection of experiences from the replay buffer, denoted as $\mathcal{N}$. For each experience $n \in \mathcal{N}$, it calculates the value of $	\hat{Q}^{\text{T}}_{i,n}$. This value represents the QoE in experience $n$ and includes a discounted Q-value of the action anticipated to be taken in the subsequent state of experience $n$, according to the network $\textit{Net}^\text{T}_i$, given by
\begin{alignat}{2}
	\hat{Q}_{i,n}^{\text{T}} = \boldsymbol{q}_i(n) + \gamma Q_i^{\text{T}}(\boldsymbol{s}_i(n+1)), \tilde{\boldsymbol{a}}_n; \theta_i^{\text{T}}),
	\label{28}  
\end{alignat}  
where $\tilde{\boldsymbol{a}}_n$ denotes the optimal action for the state $\boldsymbol{s}_i(n+1)$ based on its highest Q-value under $\textit{Net}_i^{\text{E}}$, as given by:
\begin{alignat}{2}
	\tilde{\boldsymbol{a}}_n = \text{arg} \; \max_{\boldsymbol{a} \in \mathcal{A}} \; Q_i^{\text{E}}(\boldsymbol{s}_i(n+1), \boldsymbol{a}; \theta_i^{\text{E}}).
	\label{29}  
\end{alignat} 
In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. %based on $\textit{Net}_i^{\text{T}}_i$, i.e., $\gamma Q_i^{\text{T}}(\mathcal{S}_i(i+1)), \mathcal{A}_i^{\text{N}}; \theta_i^{\text{T}})$
Based on the set $\mathcal{N}$, the EN trains the MD's neural network using previous sample experiences. Simultaneously, it updates $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ and computes $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n}, n \in \mathcal{N})$. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
\begin{alignat}{2}
	\hspace{-2mm}L(\theta_i^{\text{E}},\hat{\mathbf{Q}}_i^{\text{T}}) = {1 \over |\mathcal{N}| }\hspace{-1mm} \sum\limits_{n \in \mathcal{N}} \bigg(Q_i^{\text{E}}(\boldsymbol{s}_i(n) , \boldsymbol{a}_i(n); \theta_i^{\text{E}} ) -   \hat{Q}^{\text{T}}_{i,n}  \bigg)^2.
	\label{30}  
\end{alignat}  
In every \textit{ReplaceThreshold} iterations, the update of $\textit{Net}_i^{\text{T}}$ will involve duplicating the parameters from $\textit{Net}_i^{\text{E}}$ ($\theta_i^{T} = \theta_i^{E}$). The objective is to consistently update the network parameter $\theta_i^{T}$ in $\textit{Net}_i^{\text{T}}$, which enhances the approximation of the long-term QoE when computing the target Q-values in \eqref{28}.

\section{Performance Evaluation}
In this section, we first present the simulation setup and training configuration. We then evaluate the performance of QOCO in comparison to three baseline schemes in addition to the existing work~\cite{yang2018distributed}.
%We begin by presenting the simulation setting and training configuration, followed by the evaluation of QOCO algorithm under multiple key performance metrics in comparison to benchmark methods.
\subsection{Simulation Setup}
We consider a computation task offloading scenario involving 50 MDs and 5 ENs in the MEC environment. All the parameters are given in Table~\ref{table}. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, equivalent to 0.1 second. QOCO algorithm performs online training, incorporating real-time experience to continually improve the offloading strategy. Specifically, we employ a batch size of 16, maintain a fixed learning rate of 0.001, and set the discount factor $\gamma$ to 0.9. The probability of random exploration gradually decreases from an initial value 1, progressively approaching 0.01, all of which is facilitated by an RMSProp optimizer. %The convergence of the proposed algorithm is evaluated across a spectrum of neural network hyperparameters and algorithm configurations.
